Adaptive Video Streaming with Optimized Bitstream Extraction and PID-based Quality Control

### 2015-07-16 tmm.tex
edit a word

% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
\author{Shengbin~Meng,~Jun~Sun,~Yizhou~Duan~and~Zongming~Guo,~\em{Member,~IEEE} % <-this % stops a space
\thanks{Manuscript received July 15, 2015.}
\thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
, 100080, China (e-mail: shengbin@pku.edu.cn; sunjun@pku.edu.cn; duanyizhou@pku.edu.cn; guozongming@pku.edu.cn).}}

@@

We simulate network fluctuation by adjusting bandwidth around a certain level. We set this level from 400 to 1400 kbps to reflect different average bandwidth. All the experiments are conducted with DSS as the software platform and the bandwidth control implemented by NetLimiter 3 \cite{Netlimiter}. The baseline algorithm in the comparison refers to the packet delay feedback (PDF) algorithm in the original DSS.

@@

\begin{figure*}[t]
\centering
\subfloat[Bandwidth fluctuates around 600kbps: PSNR average and variance in the original system are 39.63 and 0.24, while in the proposed system are 39.69 (increased by 0.06) and 0.16 (reduced by 0.08).]{
\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR1.png}
\label{fig:Fluctuation-PSNR1}}\hfill
\subfloat[Bandwidth fluctuates around 800kbps: PSNR average and variance in the original system are 40.15 and 0.48, while in the proposed system are 40.62 (increased by 0.47) and 0.28 (reduced by 0.20).]{
\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR2.png}
\label{fig:Fluctuation-PSNR2}}
\qquad
\subfloat[Bandwidth fluctuates around 1000kbps: PSNR average and variance in the original system are 40.37 and 0.50, while in the proposed system are 40.74 (increased by 0.40) and 0.28 (reduced by 0.22).]{
\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR3.png}
\label{fig:Fluctuation-PSNR3}}\hfill
\subfloat[Bandwidth fluctuates around 1200kbps: PSNR average and variance in the original system are 40.48 and 0.63, while in the proposed system are 41.14 (increased by 0.66) and 0.21(reduced by 0.42).]{
\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR4.png}
\label{fig:Fluctuation-PSNR4}}
\caption{User-perceived PSNR change with time when bandwidth fluctuates \label{fig:fluctuation-psnr}}
\end{figure*}

>>>>

% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
\author{Shengbin~Meng,~Jun~Sun,~Yizhou~Duan~and~Zongming~Guo,~\em{Member,~IEEE} % <-this % stops a space
\thanks{Manuscript received May 20, 2015.}
\thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
, 100080, China (e-mail: shengbin@pku.edu.cn; sunjun@pku.edu.cn; duanyizhou@pku.edu.cn; guozongming@pku.edu.cn).}}

@@

We simulate network fluctuation by adjusting bandwidth around a certain level. We set this level from 400 to 1400 kbps to reflect different average bandwidth. All the experiments are conducted in Visual C++ 6.0 (with DSS as the software platform) and the bandwidth control is implemented by NetLimiter 3 \cite{Netlimiter}. The baseline algorithm in the comparison refers to the packet delay feedback (PDF) algorithm in the original DSS.

@@

\begin{figure*}[t]
\centering
\subfloat[Bandwidth fluctuates around 600kbps: PSNR average and variance in the original system are 39.63 and 0.24, while in the proposed system are 39.69 and 0.16.]{
\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR1.png}
\label{fig:Fluctuation-PSNR1}}\hfill
\subfloat[Bandwidth fluctuates around 800kbps: PSNR average and variance in the original system are 40.15 and 0.48, while in the proposed system are 40.62 and 0.28.]{
\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR2.png}
\label{fig:Fluctuation-PSNR2}}
\qquad
\subfloat[Bandwidth fluctuates around 1000kbps: PSNR average and variance in the original system are 40.37 and 0.50, while in the proposed system are 40.74 and 0.28.]{
\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR3.png}
\label{fig:Fluctuation-PSNR3}}\hfill
\subfloat[Bandwidth fluctuates around 1200kbps: PSNR average and variance in the original system are 40.48 and 0.63, while in the proposed system are 41.14 and 0.21.]{
\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR4.png}
\label{fig:Fluctuation-PSNR4}}
\caption{User-perceived PSNR change with time when bandwidth fluctuates \label{fig:fluctuation-psnr}}
\end{figure*}
